\chapter{Requirements}\label{ch:requirements}
This capter contains functional and non-functional requirements for Kwetterprise. Functional requirements describe what the system should do and non-functional requirements describe how the system works. \TBD{Note that this list is incomplete.}

\tereqshowid%
\tereqshowicon%

\newcommand{\pri}[1]{\hfill{\fbox{#1}}}

\section{Functional requirements}

\subsection{Tweeting}

\begin{tereqdef}{F_TWEET_POST}
    A user can post a tweet.\pri{Must}
\end{tereqdef}

\begin{tereqdef}{F_TWEET_GET_FROM_USER}
    The tweets from a user can be retrieved.\pri{Must}
\end{tereqdef}

\begin{tereqdef}{F_TWEET_REALTIME}
    An overview of real-time most recent tweets can be viewed.\pri{Should}
\end{tereqdef}

\subsubsection{Replying}

\begin{tereqdef}{F_REPLY}
    A user can reply to an existing tweet.\pri{Could}
\end{tereqdef}

\subsection{Reacting}

\begin{tereqdef}{F_REACT}
    A user can react to a tweet.\pri{Should}
\end{tereqdef}

\begin{tereqdef}{F_REACT_SHOW}
    A tweet shows the amount of reactions it has received.\pri{Should}
\end{tereqdef}

\subsection{Following}

\begin{tereqdef}{F_FOLLOW}
    A user can follow another user.\pri{Should}
\end{tereqdef}

\begin{tereqdef}{F_FOLLOW_DASH}
    A user can view a dashboard with recent tweets by followed users.\pri{Should}
\end{tereqdef}

\subsection{Users \& roles}

\begin{tereqdef}{F_REGISTER}
    A user can register themselves through a register page.\pri{Must}
\end{tereqdef}

\begin{tereqdef}{F_LOGIN}
    A user can log in.\pri{Must}
\end{tereqdef}

\begin{tereqdef}{F_LOGOUT}
    A user can logout.\pri{Must}
\end{tereqdef}

\begin{tereqdef}{F_MODERATION_DELTWEET}
    A moderator can remove tweets.\pri{Should}
\end{tereqdef}

\begin{tereqdef}{F_MODERATION_BAN}
    A moderator can ban users.\pri{Should}
\end{tereqdef}

\begin{tereqdef}{F_ADMIN_ASSIGN_ROLES}
    An administrator can change the role of a user.\pri{Should}
\end{tereqdef}

\section{\NEW{Non-functional requirements}}

\subsection{Tweeting}
\begin{tereqdef}{NF_TWEET_POST}
    The system must be able to handle 100 tweets per second.\pri{Should}
\end{tereqdef}

\begin{tereqdef}{NF_TWEET_POST_TIME}
    A tweet must be posted within 500 miliseconds.\pri{Should}    
\end{tereqdef}

\begin{tereqdef}{NF_TWEET_GET}
    The system must be able to handle to load a user's tweets 100 times per second.\pri{Should}
\end{tereqdef}

\begin{tereqdef}{NF_TWEET_REALTIME}
    A minimum of 500 real-time connections must be possible.\pri{Could}
\end{tereqdef}

\subsection{Reacting}

\begin{tereqdef}{NF_REACT_TIME}
    A reaction must be posted within 500 miliseconds.\pri{Should}
\end{tereqdef}

\subsection{API gateway}

\begin{tereqdef}{APIG_REQ}
    The API gateway must be able to handle 500 requests per second.\pri{Should}
\end{tereqdef}